### 2018-04-18 paper.Rmd
say something about MTLD

@@

Our `transcript_by_speaker` table contains multiple derived measures of lexical diversity -- here we used MTLD [@mccarthy2005assessment], a measure that is relatively robust to transcript length.
We start by filtering those children for which a sex was defined, who speak a language in our subset, and are in the appropriate age range.
We then average their MTLD score across transcripts after having grouped the data by child, age, sex, and language.

```{r echo=TRUE}
data <- stats %>%
  filter(!is.na(target_child_sex),
         language %in% included_languages) %>%
  group_by(target_child_id, target_child_age, target_child_sex, language) %>%
  filter(mtld != 0) %>%
  summarise(measure = mean(mtld)) %>%
  ungroup() %>%
  mutate(age_years = target_child_age / 365,
         target_child_sex = factor(target_child_sex, levels = c("male","female"))) %>%
  filter(age_years < max_age)
```

@@

```{r echo=FALSE, warning=FALSE}
ggplot(data, aes(x = age_years, y = measure,
                 color = target_child_sex)) +
  geom_point(alpha = .3) +
  geom_line(data = mod_data,
            aes(x = age_years, y = measure, color = target_child_sex)) +
  facet_wrap(~language) +
  ggthemes::theme_few() +
  ggthemes::scale_color_ptol(name = "Sex") +
  xlim(0,max_age) +
  ylim(0,15) +
  xlab("Age (years)") +
  ylab("MTLD") +
  theme(legend.position = "bottom")
```
This plot reveals a slight gender difference in linguistic productivity in young children, replicating the moderate female advantage found by @eriksson2012differences.
The goal of this analysis was to showcase an example of the the steps involved in using `childesr` for exploring the CHILDES dataset, as well as some of the potential hazards -- sparsity and non-independance-- that emerge in working with a diverse set of corpora, many of which were collected in longitudinal studies.

>>>>

ggplot(mlu_data %>%
         mutate(error = abs(clan - db) / clan),
       aes(error)) +
  geom_density() +
  xlim(0,.25)
```

@@

Our `transcript_by_speaker` table contains multiple derived measures of lexical diversity -- here we used MTLD [@mccarthy2005assessment].
MTLD is derived from the average length of continuous text units above a certain type-token ratio, making it relatively robust to transcript length.
We start by filtering those children for which a sex was defined, who speak a language in our subset, and are in the appropriate age range.
We then average their MTLD score across transcripts after having grouped the data by child, age, sex, and language.

```{r echo=TRUE}
data <- stats %>%
  filter(!is.na(target_child_sex),
         language %in% included_languages) %>%
  group_by(target_child_id, target_child_age, target_child_sex, language) %>%
  summarise(measure = mean(mtld)) %>%
  ungroup() %>%
  mutate(age_years = target_child_age / 365,
         target_child_sex = factor(target_child_sex, levels = c("male","female"))) %>%
  filter(age_years < max_age)
```

@@

```{r echo=FALSE, warning=FALSE}
ggplot(data, aes(x = age_years, y = measure,
                 color = target_child_sex)) +
  geom_point(alpha = .3) +
  geom_line(data = mod_data,
            aes(x = age_years, y = measure, color = target_child_sex)) +
  facet_wrap(~language) +
  ggthemes::theme_few() +
  ggthemes::scale_color_ptol(name = "Sex") +
  xlim(0,max_age) +
  ylim(0,15) +
  xlab("Age (years)") +
  ylab("MTLD") +
  theme(legend.position = "bottom")
```

This plot reveals a slight gender difference in linguistic productivity in young children, replicating the moderate female advantage found by @eriksson2012differences.
The goal of this analysis was to showcase an example of the the steps involved in using `childesr` for exploring the CHILDES dataset, as well as some of the potential hazards -- sparsity and non-independance-- that emerge in working with a diverse set of corpora, many of which were collected in longitudinal studies.
